\MakeHeader
\MakeTargetSection

% ------------------------------
% Summary
% ------------------------------

Mechanical Engineer with an M.Sc. in Additive Manufacturing and hands-on experience in mechanical design, product development, manufacturing, prototyping, and measurement-driven validation. Skilled in CAD/CAE, DFM/DFA, technical drawings, GD\&T, conventional manufacturing processes, metrology, and additive manufacturing workflows. Background includes full-cycle industrial hardware development, research-based design validation, and cross-functional work with suppliers, manufacturing teams, and technical stakeholders.

% ------------------------------
% Skills
% ------------------------------

\section{Skills}

\skill{Mechanical Design \& Product Development}{
  CAD design, assembly design, prototyping, testing \& validation, DFM/DFA, technical drawings, GD\&T, design reviews
}

\skill{Manufacturing \& Process Knowledge}{
  Machining, casting, welding, laser cutting, pressing, assembly, painting/coating, plastic/rubber injection molding, process troubleshooting
}

\skill{CAD / CAE / Engineering Software}{
  PTC Creo, Siemens NX, Autodesk Moldflow, Altair Inspire, Altair Inspire Cast, Simufact Additive, Materialise Magics, nTop
}

\skill{Additive Manufacturing}{
  SLA/MSLA, FDM, PolyJet, build preparation, support strategy, post-processing, AM process simulation
}

\skill{Metrology \& Validation}{
  CMM, profilometry, digital microscopy, dimensional inspection, calibration, tolerance analysis, failure analysis, test reporting
}

\skill{Data \& Productivity}{
  Excel, VBA, Python, NVivo
}

\skill{Languages}{
  English (Fluent), Persian (Native)
}

% ------------------------------
% Professional Experience
% ------------------------------

\section{Professional Experience}

\ExperienceHeader
{Laser Metal Additive Manufacturing Researcher}
{April 2026 -- Now}
{University of Turku, Finland}

\begin{cvitems}
  \item Contribute to a laser metal additive manufacturing research project combining technical development, commercialization, and market validation.
  \item Conduct stakeholder and expert interviews with potential users, partners, and industry contacts to capture application needs, adoption barriers, and technical requirements.
  \item Analyze qualitative interview data using NVivo to identify customer segments, early adopters, use-case priorities, and market feedback patterns.
  \item Support market research, competitor analysis, and commercialization planning for laser metal AM applications.
  \item Prepare IP-related documentation, project deliverables, and structured inputs for future technical development planning.
\end{cvitems}

\ExperienceHeader
{Master Thesis Student -- Manufacturing / Additive Manufacturing Engineering}
{April 2025 -- December 2025}
{Karl Storz (Medical Devices Manufacturer), Estonia}

\begin{cvitems}
  \item Developed and evaluated additive-manufacturing-supported tooling concepts for manufacturing validation of small, thin-walled polymer components.
  \item Designed mold insert assemblies, parting surfaces, and alignment/slider concepts in PTC Creo, balancing manufacturability, access, assembly constraints, and demolding behavior.
  \item Used Autodesk Moldflow to evaluate gate location, pressure/flow feasibility, and process behavior of physical trials.
  \item Conducted structured experimental trials and metrology-based evaluation using CMM, microscopy, and profilometry to identify dimensional deviations, deformation, adhesion, and failure modes.
  \item Converted experimental and measurement findings into design and process recommendations for improving repeatability, manufacturability, and practical tooling performance.
\end{cvitems}

\ExperienceHeader
{Research Assistant -- Photonic Measurement Systems}
{October 2024 -- March 2025}
{Institute of Production Engineering and Photonic Technologies - TU Wien, Austria}

\begin{cvitems}
  \item Designed and fabricated precision opto-mechanical fixtures for cylindrical and curved samples, improving measurement stability and focal alignment.
  \item Developed rotary and linear motion stages to enable controlled dynamic measurement workflows for foils, vials, and PET bottles.
  \item Operated and optimized real-time imaging ellipsometry setups for thin-film analysis on moving webs and complex geometries.
  \item Processed measurement data using in-house software and benchmarked sensor performance against commercial laboratory equipment.
\end{cvitems}

\ExperienceHeader
{Mechanical Engineer \& Co-founder}
{August 2020 -- August 2023}
{Atron (Hardware Startup -- Industrial Control Equipment)}

\begin{cvitems}
  \item Co-founded an industrial gas equipment startup and contributed to the launch of its first product, an Industrial Gas Pressure Regulator, after an 18-month development cycle.
  \item Led mechanical design and product development for a regulator assembly with 60+ components, taking concepts through CAD design, prototyping, manufacturing coordination, testing, assembly, and delivery.
  \item Applied DFM/DFA and manufacturing planning across conventional processes, including casting, rubber injection molding, CNC machining, laser cutting, pressing, assembly, and painting/coating.
  \item Coordinated suppliers and manufacturing partners for component fabrication, tooling, material selection, quality control, and production troubleshooting.
  \item Supported technical communication, product delivery, and customer coordination through a Tehran-based distributor and direct industrial clients, including IKCO, Golgohar Mining \& Industrial, and SSECO.
\end{cvitems}

\ExperienceHeader
{Mechanical Engineer \& Operations Supervisor}
{July 2018 -- July 2020}
{Novin Technic (Manufacturer of display systems for textiles and flooring)}

\begin{cvitems}
  \item Collaborated with the engineering team to improve existing products and support new developments, creating technical documentation and process standards.
  \item Coordinated production workflows and inventory management to streamline manufacturing execution and improve delivery reliability.
  \item Developed analytical tools (Excel-based) for production scheduling and cost analysis, enhancing operational efficiency and resource planning.
  \item Supported technical communication for international exhibitions and customers, ensuring alignment on product specifications and requirements.
\end{cvitems}

% ------------------------------
% Education
% ------------------------------

\section{Education}

\ExperienceHeader
{M.Sc. Additive Manufacturing}
{2023 -- 2025}
{Aalto University (Finland) \& Vienna University of Technology (Austria) -- GPA 4.7/5}
\begin{cvitems}
  \item Dean’s List (Aalto School of Engineering, 2023--2024)
  \item EIT Manufacturing scholarship recipient
  \item 3rd place (Team BikePark), Rail Innovation Challenge by FERROCAMPUS (France, 2024)
\end{cvitems}

\ExperienceHeader
{B.Sc. Mechanical Engineering}
{2009 -- 2014}
{Azad University}

\ExperienceHeader
{B.Sc. Industrial Management}
{2010 -- 2015}
{Payam Noor University}